Dimensions of the impacts of land transitions in the Amazon and Cerrado

### 2023-03-20 manuscript/lct_se_ac.qmd
Small fix.
Change map figure. Rewrite Conclusions.

---
title: "Dimensions of the impacts of land transitions in the Amazon and Cerrado"
author: 
  - name: Hugo Tameirão Seixas
    email: seixas.hugo@protonmail.com
    url: hugotseixas.com
    affiliations:
      - name: State University of Campinas
format: 
  html:
    theme: lux
page-layout: article
bibliography: references.bib
link-citations: true
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto
  cache: true
license: CC BY-NC-ND 4.0
self-contained: true
---

@@

library(sf)
library(geobr)
library(gt)
library(DiagrammeR)
library(lubridate)
library(tidyverse)

@@

The choice of models will depend on a series of tests, accounting the accuracy and adequacy of the model to the theory.

@@

```{r}
#| label: grid-map-figure
#| echo: false
#| message: false

biomes <- read_biomes(showProgress = FALSE) %>%
  filter(name_biome %in% c("Amazônia", "Cerrado")) %>%
  st_make_valid()

grid <- 
  st_make_grid(biomes, cellsize = 0.2) %>%
  st_as_sf() %>%
  st_filter(biomes, .predicate = st_intersects)

ggplot() +
  geom_sf(data = biomes) +
  geom_sf(data = grid, fill = "transparent") +
  theme_void()

@@

The data will be stored in a nested directories structured database with hive-style partitioning. 
The database will be composed of a collection of parquet files, a format with high compression, that facilitates processing large volumes of data.
The main partition will be the variables, which means that each variable will be stored in a separate directory.
If necessary, the data will be partitioned by further variables (as a rule of thumb, each parquet file should not be smaller than 20MB and not bigger than 2GB).

@@

The main objective of the project is to delve deeper into the reasons behind vegetation removals and assess their impact on the environment and human well-being. 
This effort has the potential to provide valuable insights into what can reduce the negative consequences after vegetation removal. 
By thoroughly investigating the causes of vegetation removal and its effects, the project aims to contribute to a better understanding of this complex issue and to identify strategies for mitigating its negative impact. 
The end goal is to ensure that future vegetation removal is carried out in a way that minimizes harm to the environment and supports the well-being of people who depend on it.

>>>>

---
title: "Dimensions of the impacts of land transitions in the Amazon and Cerrado"
author: 
  - name: Hugo Tameirão Seixas
    email: seixas.hugo@protonmail.com
    url: hugotseixas.com
    affiliations:
      - name: State University of Campinas
format: 
  html:
    theme: lux
    page-layout: article
toc: true
bibliography: references.bib
link-citations: true
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto
  cache: true
license: CC BY-NC-ND 4.0
self-contained: true
---

@@

library(gt)
library(DiagrammeR)
library(lubridate)
library(tidyverse)

@@

@@

![Representation of the spatial grid that will be used to store the data from different sources.](figs/grid_cells.png)

@@

The data will be stored in a nested directories database with hive-style partitioning. 
The database will be composed of a collection of parquet files, a format with high compression, that facilitates processing large volumes of data.
The main partition will be the variables, which means that each variable will be stored in a separate directory.
If necessary, the data will be partitioned by further variables (as a rule of thumb, each parquet file should not be smaller than 20MB and not bigger than 2GB).

@@

The final outcome of this project is expected to provide answers to the following questions as concluding remarks:

- How suitable were the models to represent the studied phenomena?

The final remarks should summarize the potential of utilizing observed data and statistical models to estimate the causes and impacts of deforestation, as also explore the limitations of this method.

- What are the implications of the results to the development of public policies in the Amazon and Cerrado biomes?

Assuming that the models were suitable for representing the phenomena, the concluding remarks will summarize how the results can inform important variables that need to be taken into account for the development of public policies. Spatialization may also prove useful by providing regions that are more suitable for different kinds of strategies to mitigate deforestation and its impacts.
